Part B-2

### 2024-05-30 msca-pf-part-b1-template.tex
feat: update templates for 2024 call

% NOTE: this needs to be kept so that the sections match the template!
\setcounter{section}{1}

@@

\section{Excellence}

\subsection{Quality and pertinence of the project's research and innovation objectives}

@@

\subsection{Soundness of the proposed methodology}

@@

    \item \emph{Gender dimension and other diversity aspects}: Describe how the
    gender dimension and other diversity aspects are taken into account in the
    project's research and innovation content. If you do not consider such a
    gender dimension to be relevant in your project, please provide a
    justification.
    \begin{itemize}
        \item Remember that that this question relates to the content of the
        planned research and innovation activities, and not to gender balance
        in the teams in charge of carrying out the project.

@@

    Please also see the “how to evaluate open science in Horizon Europe proposals”
    video on the \href{https://ec.europa.eu/info/funding-tenders/opportunities/portal/screen/support/videos}{Funding \& Tenders portal}.
\end{itemize}

@@

    \item Rationale and added-value of the non-academic placement (if applicable).
\end{itemize}

@@

\section{Impact}

@@

\subsection{Suitability and quality of the measures to maximise expected
outcomes and impacts, as set out in the dissemination and exploitation plan,
including communication activities}

@@

    \item Be specific, referring to the effects of your project, and not R\&I
    in general in this field. State the target groups that would benefit.
Partial alignment of text with standard application form template for criteria 2.3
    \begin{itemize}
        \item \emph{Expected scientific impact(s)}: e.g. contributing to specific
        scientific advances, across and within disciplines, creating new knowledge,
        reinforcing scientific equipment and instruments, computing systems (i.e.
        research infrastructures);

        \item \emph{Expected economic/technological impact(s)}: e.g. bringing new
        products, services, business processes to the market, increasing efficiency,
        decreasing costs, increasing profits, contributing to standards’ setting,
        etc.

        \item \emph{Expected societal impact(s)}: e.g. decreasing CO2 emissions,
        decreasing avoidable mortality, improving policies and decision-making,
        raising consumer awareness.
    \end{itemize}

@@

    \item Give an indication of the magnitude and importance of the project's
    contribution to the expected outcomes and impacts, should the project be
    successful. Provide quantified estimates where possible and meaningful.

@@

\section{Quality and Efficiency of the Implementation}

@@

A Gantt chart must be included and should indicate the proposed Work Packages
(WP), major deliverables, milestones, secondments, placements. This Gantt chart
counts towards the 10-page limit. The schedule in the Gantt chart should indicate
the number of months elapsed from the start of the action (Month 1).

@@

    \item Quality and capacity of the participating organisations, including
    infrastructure, logistics and facilities should be outlined in Part B-2
    Section 5 (``Capacity of the Participating Organisations'').
\end{itemize}

@@

>>>>

% NOTE: this needs to be kept so that the sections match the template!
\setcounter{section}{0}

@@

\section{Excellence}
\label{REL-EVA-RE}

\subsection{
    Quality and pertinence of the project's research and innovation objectives
    (and the extent to which they are ambitious, and go beyond the state of the art)}

@@

\subsection{
    Soundness of the proposed methodology
    (including interdisciplinary approaches, consideration of the gender
    dimension and other diversity aspects if relevant for the research project,
    and the quality of open science practices)}

@@

    \item \emph{Gender dimension and other diversity aspects}: Describe how the
    gender dimension and other diversity aspects are taken into account in the
    project's research and innovation content. If you do not consider such a
    gender dimension to be relevant in your project, please provide a
    justification.
    \begin{itemize}
        \item Remember that that this question relates to the \emph{content} of the
        planned research and innovation activities, and not to gender balance
        in the teams in charge of carrying out the project.

@@

    Please also see the “how to evaluate open science in Horizon Europe proposals”
    video on the \href{https://ec.europa.eu/info/funding-tenders/opportunities/portal/screen/support/videos}{Funding \& Tenders portal} and
    \href{https://rea.ec.europa.eu/open-science_en}{Open Science - European Commission (europa.eu)}.
\end{itemize}

@@

    \item Rationale and added-value of the non-academic placement (if applicable)
    and secondment (if applicable).
\end{itemize}

@@

\section{Impact}
\label{IMP-ACT-IA}

@@

\subsection{Suitability and quality of the measures to maximise expected
outcomes and impacts, as set out in the dissemination and exploitation plan,
including communication activities}
\label{COM-DIS-VIS-CDV}

@@

    \item Be specific, referring to the effects of your project, and not R\&I
    in general in this field. State the target groups that would benefit.

    \item The impacts of your project may be:

    \begin{itemize}
        \item \emph{Scientific}: e.g. contributing to specific scientific advances,
        across and within disciplines, creating new knowledge, reinforcing
        scientific equipment and instruments, computing systems (i.e. research
        infrastructures);

        \item \emph{Economic/technological}: e.g. bringing new
        products, services, business processes to the market, increasing efficiency,
        decreasing costs, increasing profits, contributing to standards’ setting,
        etc.

        \item \emph{Societal}: e.g. decreasing CO2 emissions,
        decreasing avoidable mortality, improving policies and decision-making,
        raising consumer awareness.
    \end{itemize}

@@

    \item Give an indication of the magnitude and importance of the project's
    contribution to the expected outcomes and impacts, should the project be
    successful. Provide credible quantified estimates where possible and meaningful.

@@

\section{Quality and Efficiency of the Implementation}
\label{WRK-PLA-WP}

@@

A Gantt chart must be included and should indicate the proposed Work Packages
(WP), major deliverables, milestones, secondments, placements, if applicable.
This Gantt chart counts towards the 10-page limit.

The schedule in the Gantt chart should indicate the number of months elapsed
from the start of the action (Month 1).

@@

    \item Quality and capacity of the participating organisations, including
    infrastructure, logistics and facilities. Additional information should be
    outlined in Part B-2 Section 5 (``Capacity of the Participating Organisations'').
\end{itemize}

@@

% kate: default-dictionary en_GB;

### 2024-05-30 msca-pf-part-b2-template.tex
feat: update templates for 2024 call

Applicants who have successfully defended their doctoral thesis before the call
deadline but who have not yet formally been awarded the doctoral degree must
clearly indicate the date of the successful PhD defence (``viva''). Researchers
having their last thesis defence after the call deadline will be automatically
declared ineligible for this call.

@@

Applicants should provide additional information regarding the administrative/legal
relations between the department carrying out the work as described in the table
below, and the entity/entities mentioned in Part A of the proposal (i.e. linked
to the given Participant Identification Code – PIC).

@@

Please complete a separate table for each participating organisation. For the
beneficiary, this table should be maximum 1 page in length; for each associated
partner, the table should be maximum ½ page in length. Choose one of

@@

\begin{msclongtable}[\small]{
    |>{\ra}p{0.3\linewidth}
    |>{\ra}p{0.66\linewidth}|}
\hline
\multicolumn{2}{|l|}{
    \textbf{[Role]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{[Full name + Legal Entity Short Name + Country]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{General description}
} \\
\hline
\textbf{Role and profile of supervisor} & \\
\hline
\textbf{Key research facilities, infrastructure and equipment} &
Demonstrate that the beneficiary has sufficient facilities and infrastructure to host and/or offer a suitable environment for training and transfer of knowledge to the recruited experienced researcher.

If applicable, indicate the name of the associated partner linked to a beneficiary and describe the nature of the link in the corresponding table. \\
\hline
\textbf{Previous and current involvement in EU-funded research and training
programmes/actions/projects} &
Indicate up to 5 relevant EU, national or international research and training
actions/projects in which the institution/department has previously participated
and/or is currently participating. \\
\hline
\end{msclongtable}

@@

Please explain how the proposed project would strive to adhere to the MSCA Green
Charter\footnotemark{} during its implementation.

\footnotetext{MSCA Green Charter \url{https://ec.europa.eu/msca/green_charter}.
While the MSCA Green Charter is non-binding and adherence to it will not be
subject to evaluation, funded projects are strongly encouraged to take into
account the principles it sets out.}

\section{Required for Global Fellowships only: Letter(s) of commitment from
    associated partners (hosting of the outgoing phase)}

@@

I undersigned \emph{[title, first name and surname]}, in my quality of
\emph{[role in the organisation]} in \emph{[name of the organisation]} commit
to set up all necessary provisions to participate as associated partner in the
proposal \emph{[proposal number and/or acronym]} submitted to the call
HE-MSCA-PF-2023, should the proposal be funded.

>>>>

Applicants who have successfully defended their doctoral thesis \emph{before} the call
deadline but who have not yet formally been awarded the doctoral degree must
clearly indicate the date of the successful PhD defence (``viva''). Researchers
having their last thesis defence after the call deadline will be automatically
declared ineligible for this call.

@@

Applicants should provide additional information regarding the administrative/legal
relations between the department carrying out the work as described in the table
below, and the entity/entities mentioned in Part A of the proposal (i.e. linked
to the given Participant Identification Code –- PIC).

@@

Please complete a separate table for each participating organisation. For the
beneficiary, this table should be \emph{maximum 1 page in length}; for each associated
partner, the table should be \emph{maximum ½ page in length}. Choose one of

@@

\begin{msclongtable}[\small]{
    |>{\ra}p{0.3\linewidth}
    |>{\ra}p{0.66\linewidth}|}
\hline
\multicolumn{2}{|l|}{
    \textbf{[Role]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{[Full name + Legal Entity Short Name + Country]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{General description}
} \\
\hline
\textbf{Role and profile of supervisor} & \\
\hline
\textbf{Key research facilities, infrastructure and equipment} &
\emph{Demonstrate that the beneficiary has sufficient facilities and infrastructure
to host and/or offer a suitable environment for training and transfer of knowledge
to the recruited experienced researcher.}

\bigskip

\emph{If applicable, indicate the name of the associated partner linked to a beneficiary
and describe the nature of the link in the corresponding table.} \\
\hline
\textbf{Previous and current involvement in EU-funded research and training
programmes/actions/projects} &
\emph{Indicate up to 5 relevant EU, national or international research and training
actions/projects in which the institution/department has previously participated
and/or is currently participating.} \\
\hline
\end{msclongtable}

@@

Please explain how the proposed project would strive to adhere to the MSCA Green
Charter\footnotemark{} during its implementation. Please indicate here --
max 1/2 page -- what actions you propose to take to ensure the sustainable
implementation of project and to mitigate its environmental impact, in line
with the principles set out in the MSCA Green Charter.

\footnotetext{MSCA Green Charter \url{https://ec.europa.eu/msca/green_charter}.}

\section{
    Required for Global Fellowships only: Letter(s) of commitment from
    associated partners (hosting of the outgoing phase)}

@@

I undersigned \emph{[title, first name and surname]}, in my quality of
\emph{[role in the organisation]} in \emph{[name of the organisation]} commit
to set up all necessary provisions to participate as associated partner in the
proposal \emph{[proposal number and/or acronym]} submitted to the call
HE-MSCA-2024-PF, should the proposal be funded.
